Yeast Deamination Sequence and Position Figure Generation

### 2022-06-15 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update yeast notebooks
- Support for all_reps
- Read length counting occurs during data generation

expansionOffset = 10
cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
minReadLength = 22; maxReadLength = 25

>>>>

expansionOffset = 10
cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 22; maxReadLength = 25

### 2022-06-15 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
Update yeast notebooks
- Support for all_reps
- Read length counting occurs during data generation

cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
minReadLength = 22; maxReadLength = 25

>>>>

cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 22; maxReadLength = 25
